Comets in star clusters: I. Dynamics of free-floating comets

### 2018-01-18 paper.tex
rm unused files; add necessary define for \apj, \apjl...; change bibliography to apj style

@@

%-------------------------------------------------------------------
%   bibliography
%-------------------------------------------------------------------
\clearpage
%\phantomsection\
%\bibliographystyle{apj} 
\bibliographystyle{mn2e} 
\bibliography{Qi}

>>>>

\def\aj{AJ}          % Astronomical Journal
\def\actaa{Acta Astron.}          % Acta Astronomica
\def\araa{ARA\&A}          % Annual Review of Astron and Astrophys
\def\apj{ApJ}          % Astrophysical Journal
\def\apjl{ApJ}          % Astrophysical Journal, Letters
\def\apjs{ApJS}          % Astrophysical Journal, Supplement
\def\ao{Appl.~Opt.}          % Applied Optics
\def\apss{Ap\&SS}          % Astrophysics and Space Science
\def\aap{A\&A}          % Astronomy and Astrophysics
\def\aapr{A\&A~Rev.}          % Astronomy and Astrophysics Reviews
\def\aaps{A\&AS}          % Astronomy and Astrophysics, Supplement
\def\azh{AZh}          % Astronomicheskii Zhurnal
\def\baas{BAAS}          % Bulletin of the AAS
\def\bac{Bull. astr. Inst. Czechosl.}          % Bulletin of the Astronomical Institutes of Czechoslovakia
\def\caa{Chinese Astron. Astrophys.}          % Chinese Astronomy and Astrophysics
\def\cjaa{Chinese J. Astron. Astrophys.}          % Chinese Journal of Astronomy and Astrophysics
\def\icarus{Icarus}          % Icarus
\def\jcap{J. Cosmology Astropart. Phys.}          % Journal of Cosmology and Astroparticle Physics
\def\jrasc{JRASC}          % Journal of the RAS of Canada
\def\mnras{MNRAS}          % Monthly Notices of the RAS
\def\memras{MmRAS}          % Memoirs of the RAS
\def\na{New A}          % New Astronomy
\def\nar{New A Rev.}          % New Astronomy Review
\def\pasa{PASA}          % Publications of the Astron. Soc. of Australia
\def\pra{Phys.~Rev.~A}          % Physical Review A: General Physics
\def\prb{Phys.~Rev.~B}          % Physical Review B: Solid State
\def\prc{Phys.~Rev.~C}          % Physical Review C
\def\prd{Phys.~Rev.~D}          % Physical Review D
\def\pre{Phys.~Rev.~E}          % Physical Review E
\def\prl{Phys.~Rev.~Lett.}          % Physical Review Letters
\def\pasp{PASP}          % Publications of the ASP
\def\pasj{PASJ}          % Publications of the ASJ
\def\qjras{QJRAS}          % Quarterly Journal of the RAS
\def\rmxaa{Rev. Mexicana Astron. Astrofis.}          % Revista Mexicana de Astronomia y Astrofisica
\def\skytel{S\&T}          % Sky and Telescope
\def\solphys{Sol.~Phys.}          % Solar Physics
\def\sovast{Soviet~Ast.}          % Soviet Astronomy
\def\ssr{Space~Sci.~Rev.}          % Space Science Reviews
\def\zap{ZAp}          % Zeitschrift fuer Astrophysik
\def\nat{Nature}          % Nature
\def\iaucirc{IAU~Circ.}          % IAU Cirulars
\def\aplett{Astrophys.~Lett.}          % Astrophysics Letters
\def\apspr{Astrophys.~Space~Phys.~Res.}          % Astrophysics Space Physics Research
\def\bain{Bull.~Astron.~Inst.~Netherlands}          % Bulletin Astronomical Institute of the Netherlands
\def\fcp{Fund.~Cosmic~Phys.}          % Fundamental Cosmic Physics
\def\gca{Geochim.~Cosmochim.~Acta}          % Geochimica Cosmochimica Acta
\def\grl{Geophys.~Res.~Lett.}          % Geophysics Research Letters
\def\jcp{J.~Chem.~Phys.}          % Journal of Chemical Physics
\def\jgr{J.~Geophys.~Res.}          % Journal of Geophysics Research
\def\jqsrt{J.~Quant.~Spec.~Radiat.~Transf.}          % Journal of Quantitiative Spectroscopy and Radiative Trasfer
\def\memsai{Mem.~Soc.~Astron.~Italiana}          % Mem. Societa Astronomica Italiana
\def\nphysa{Nucl.~Phys.~A}          % Nuclear Physics A
\def\physrep{Phys.~Rep.}          % Physics Reports
\def\physscr{Phys.~Scr}          % Physica Scripta
\def\planss{Planet.~Space~Sci.}          % Planetary Space Science
\def\procspie{Proc.~SPIE}          % Proceedings of the SPIE
\let\astap=\aap
\let\apjlett=\apjl
\let\apjsupp=\apjs
\let\applopt=\ao

@@

%-------------------------------------------------------------------
%   bibliography
%-------------------------------------------------------------------
\clearpage
%\phantomsection\
\bibliographystyle{apj} 
%\bibliographystyle{mn2e} 
\bibliography{Qi}
